Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source, particularly for researchers seeking to apply machine learning to the vast collections of digitized specimens. Unfortunately, the available metadata is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means.
This paper reports on research that applies machine-driven approaches to
analyzing digitized fish images and extracting various of important
features from them. The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. Automatically generated metadata is crucial for identifying
the high-quality images needed for the neural network's predictive
analyses.
%predictive analytics?
Methods that  combine machine learning  and  image  informatics techniques allow us to rapidly enrich the existing metadata associated with each of the
7,244 images from the Illinois Natural History Survey (INHS). The sample
images each include 22 manually generated metadata properties, which
aid our study.  Results show we can  accurately generate metadata for
twenty key %6? 
metadata properties, for example: fish quantity, fish orientation,
image scaling based on
ruler identification and measurement, and general image quality metrics
(brightness and contrast). Results also show can also x, y, z.
%to confirm list of six properties.
%x, y, z = any other key results. jg will add from results section, unless someone else does first. 
The automatic process out-performs humans in terms of time and labor cost,
as well as accuracy, and provides a novel solution for leveraging digitized
specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
%world wide [*across the globe] or we may not even need this part as open access is global access

% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}

@@

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and machine learning algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %machine learning? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure*}
  \centering
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure*}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.

@@

Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}. The camera's technical metadata is automatically captured and inserted into digital image files at the time of acquisition. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting. Even so, the majority of automatically registered technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
Fish image analysis research, as reviewed below, demonstrates the
potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of machine learning.

@@

% Scientific studies on species identification in fish have considerable significance in aquatic ecosystems and quality evaluation. The morphological differences between different fish species are obvious. Machine learning methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective. Recently, deep learning-based identification of fish species has been widely used. However, fish species identification still faces many challenges due to the small scale of fish samples and the imbalance of the number of categories. For example, the model is prone to being overfitted, and the performance of the classifier is biased to the fish species of most samples. To solve the above problems, this paper proposes a fish species identification approach based on SE-ResNet152 and class-balanced focal loss. First, visualization analysis and image preprocessing of fish datasets are carried out. Second, the SE-ResNet152 model is constructed as a generalized feature extractor and is migrated to the target dataset. Finally, we apply the class-balanced focal loss function to train the SE-ResNet152 model, and realize fish species identification on three fish image views (body, head, and scale). The proposed method was tested on the Fish-Pak public dataset and achieved 98.80%, 96.67%, and 91.25% accuracy on the three fish image views, respectively. To ensure the superior performance of the proposed method, we performed an experimental comparison with other methods involving SENet154, DenseNet121, ResNet18, ResNet152, VGG16, cross-entropy, and focal loss. Comprehensive empirical analyses reveal that the proposed method achieves good performance on the three fish image views and outperforms common methods.

@@

The research reviewed above involves image features extraction and
artificial intelligence; although the researchers have not applied these
approaches to the burgeoning collections of digitized specimens
accessible in open repositories. Our research addresses this need by
applying machine learning and image informatics techniques to extract key
metadata properties from fish specimen images and computing
higher-level metadata based on these initial results.
Our goals and objectives our presented below.

@@

<--NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories. Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results. Our goals and objectives are presented in the following section.
\end{comment}

%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of machine learning, image processing and image informatics techniques to extract key metadata properties from the images. These properties a critical for selecting high-quality, usable digitized specimens for further computational analysis, and and ensuring that the specimen images meet both scientific and technical requirements.

@@

Digitized specimens accessible in open-access repositories provide a rich,
extensive data source for machine learning and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by
% combining machine learning and image informatics techniques to produce
developing a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, one that is
prohibitively costly in both terms of labor and time. Additionally, our
methods collectively provide a novel and general approach to computing
higher-level metadata that will support scientific inquiry based
on the analysis of specimen image collections.

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for three example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

\section{Methods}
Our process for metadata generation can be divided into three steps: 1) object detection with Facebook's Detectron2 machine learning library (referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
% \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}

@@

\section{Conclusions}
The BGNN project demonstrates a clear need for improved metadata associated with specimen image collections. Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited. Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.

In this paper we presented such a metadata generation program. Using machine learning and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy. It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information. Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data. Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
\subsection{Future Work}
The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask. A deficiency of the current process is that it only operates on single channel intensity. Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background. Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features. Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.

>>>>

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens. Unfortunately, the available metadata is often sparse and, at times, erroneous. Additionally, it is prohibitively expensive to address these limitations through traditional, manual means.
This paper reports on research that applies machine-driven approaches to
analyzing digitized fish images and extracting various important
features from them. The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. Automatically generated metadata is crucial for identifying
the high-quality images needed for the neural network's predictive analytics.
%predictive analytics?
Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with each of 
7,244 images from the Illinois Natural History Survey (INHS). The sample
images all have 22 manually generated metadata properties associated with them, which
aid our study.  Results show we can accurately generate many key metadata properties relevant to the
BGNN project such as: fish quantity and orientation,  image scaling based on
ruler identification and measurement, and general image quality metrics
(e.g.\ brightness and contrast). Results also show we can also accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analysis.
%to confirm list of six properties.
%x, y, z = any other key results. jg will add from results section, unless someone else does first. 
The automatic process out-performs humans in terms of time and labor cost,
as well as accuracy, and provides a novel solution for leveraging digitized
specimens in ML. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
%world wide [*across the globe] or we may not even need this part as open access is global access

% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent ML, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of ML and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}

@@

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying ML and making new scientific discoveries.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and ML algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure*}
  \centering
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure*}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of ML and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.

@@

Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}. The camera's technical metadata is automatically captured and inserted into digital image files at the time of acquisition. Some of this metadata may be useful when selecting a ML sample. A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting. Even so, the majority of automatically registered technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
Fish image analysis research, as reviewed below, demonstrates the
potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of ML.

@@

% Scientific studies on species identification in fish have considerable significance in aquatic ecosystems and quality evaluation. The morphological differences between different fish species are obvious. ML methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective. Recently, deep learning-based identification of fish species has been widely used. However, fish species identification still faces many challenges due to the small scale of fish samples and the imbalance of the number of categories. For example, the model is prone to being overfitted, and the performance of the classifier is biased to the fish species of most samples. To solve the above problems, this paper proposes a fish species identification approach based on SE-ResNet152 and class-balanced focal loss. First, visualization analysis and image preprocessing of fish datasets are carried out. Second, the SE-ResNet152 model is constructed as a generalized feature extractor and is migrated to the target dataset. Finally, we apply the class-balanced focal loss function to train the SE-ResNet152 model, and realize fish species identification on three fish image views (body, head, and scale). The proposed method was tested on the Fish-Pak public dataset and achieved 98.80%, 96.67%, and 91.25% accuracy on the three fish image views, respectively. To ensure the superior performance of the proposed method, we performed an experimental comparison with other methods involving SENet154, DenseNet121, ResNet18, ResNet152, VGG16, cross-entropy, and focal loss. Comprehensive empirical analyses reveal that the proposed method achieves good performance on the three fish image views and outperforms common methods.

@@

The research reviewed above involves image features extraction and
artificial intelligence; although the researchers have not applied these
approaches to the burgeoning collections of digitized specimens
accessible in open repositories. Our research addresses this need by
applying ML and image informatics techniques to extract key
metadata properties from fish specimen images and computing
higher-level metadata based on these initial results.
Our goals and objectives our presented below.

@@

<--NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories. Our research addresses this need by applying ML and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results. Our goals and objectives are presented in the following section.
\end{comment}

%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of ML, image processing and image informatics techniques to extract key metadata properties from the images. These properties a critical for selecting high-quality, usable digitized specimens for further computational analysis, and and ensuring that the specimen images meet both scientific and technical requirements.

@@

Digitized specimens accessible in open-access repositories provide a rich,
extensive data source for ML and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by
% combining ML and image informatics techniques to produce
developing a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, one that is
prohibitively costly in both terms of labor and time. Additionally, our
methods collectively provide a novel and general approach to computing
higher-level metadata that will support scientific inquiry based
on the analysis of specimen image collections.

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for three example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

\section{Methods}
Our process for metadata generation can be divided into three steps: 1) object detection with Facebook's Detectron2 ML library (referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
% \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}

@@

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to perform advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before. Our investigation has thus far focused on fish as the specimen of study. Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase}, and likely many more undiscovered. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype information. The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata. Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to still be somewhat limited. This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them. Object detection as explored in our research, working with an established architecture, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research. And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.
%can we say something here.

Digital libraries serve to collect, provide access to, and archive rich collections of a wide array of materials. Many digital libraries interconnect with open repository, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)~\cite{wilkinson2016fair}. In discussing the future of digital library services \cite{fox2021building} underscores the need to prepare for and test ML applications. The work presented here, within the context of the BGNN project, demonstrates a clear need for improved metadata associated with specimen image collections. Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and ML is limited. Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.

\section{Conclusion}
In this paper we presented such a metadata generation program. Using ML and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy. It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information. Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data. Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
\subsection{Future Work}
The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask. A deficiency of the current process is that it only operates on single channel intensity. Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background. Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features. Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
